---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---
 
Loading required libraries and packages.
 
```{r, echo=FALSE, include=FALSE}
library(knitr)
library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
library(tidyverse)
library(data.table)
library(readxl)
library(ggpubr)
library(xtable)
library(car)
library(rcompanion)
library(MASS)
library(rstatix)
library(bestNormalize)
library(pixiedust)

opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
wd = '/Volumes/HIV/HIV/HIV_newsubjects/'
```
 
Setting up ROI rsCVR dataframe.
 
```{r, echo=FALSE}
results <- read.csv(paste0(wd, 'FunImg/Results_minor_all_subs.csv'), header=FALSE)
subject_names <- read.csv(paste0(wd, 'FunImg/subject_list_all_subs.csv'), header=FALSE)
whole_roi_names <- c("Frontal", "Parietal", "Temporal", "Limbic", "Occipital", "Insula", "BasalGanglia", "Thalamus", "BasalForebrain", "Midbrain", "Cerebellum", "SFG", "SFG_PFC", "SFG_pole", "MFG", "MFG_DPFC", "IFG_opercularis", "IFG_orbitalis", "IFG_triangularis", "LFOG", "MFOG", "RG", "PoCG", "PrCG", "SPG", "SMG", "AG", "PrCu", "STG", "STG_pole", "MTG", "MTG_pole", "ITG", "PHG", "ENT", "FuG", "SOG", "MOG", "IOG", "Cu", "LG", "rostral_ACC", "subcallosal_ACC", "subgenual_ACC", "dorsal_ACC", "PCC", "Insula_minor", "Amygdala", "Hippocampus", "Caudate", "Putamen", "GP", "Thalamus_minor", "Hypothalamus", "AnteriorBasalForebrain", "NucleusAccumbens", "RedNucleus", "SubstantiaNigra", "CerebellumGM", "CP", "Midbrain_minor", "CST", "SCP", "MCP", "PCT", "ICP", "ML", "Pons_minor", "Medulla_minor", "ACR", "SCR", "PCR", "GCC", "BCC", "SCC", "PVWl", "ALIC", "PLIC", "RLIC", "EC", "CGC", "CGH", "FxST", "Fx", "IFO", "PTR", "SS", "SFO", "SLF", "Cl", "PosteriorBasalForebrain", "Mammillary", "OpticTract", "PVWa", "PVWp", "SFWM", "SFWMPFC", "SFWMpole", "MFWM", "MFWM_DPFC", "IFWM_opercularis", "IFWM_orbitalis", "IFWM_triangularis", "LFOWM", "MFOWM", "FGWM", "PoCWM", "PrCWM", "SPWM", "SMWM", "AGWM", "PrCuWM", "STWM", "STWM_pole", "MTWM", "MTWM_pole", "ITWM", "FuWM", "SOWM", "MOWM", "IOWM", "CuWM", "LGWM", "rostralWM_ACC", "subcallosalWM_ACC", "subgenualWM_ACC", "dorsalWM_ACC", "PCCWM", "CerebellumWM", "MCP_cb", "ICP_cb", "FrontSul", "CentralSul", "SylFrontSul", "SylTempSul", "SylParieSul", "ParietSul", "CinguSul", "OcciptSul", "TempSul", "Chroid_LVetc", "ECC", "ECSAnterior", "ECSPosterior")
major_roi_names <- c("Frontal", "Parietal", "Temporal", "Limbic", "Occipital", "Insula", "BasalGanglia", "Thalamus", "BasalForebrain", "Midbrain", "Cerebellum")
names(results) <- whole_roi_names
row.names(results) <- t(subject_names)
```
 
Setting up demographic and other information dataframes.
 
```{r}
group_list = read_excel(paste0(wd, 'HIV_toba_resting_160.xlsx'), na="na")
# group_list$`HIVDuration(mons)` <- as.numeric(as.character(group_list$`HIVDuration(mons)`))
subset_group_list <- group_list[which(group_list$folder%in%as.character(subject_names$V1)), ]
row.names(subset_group_list) <- subset_group_list$folder
```
 
Set up final combined dataframe including all Variables of Interest.
 
```{r}
final_df <- merge(results, subset_group_list,by="row.names")
final_df_new <- final_df %>%
  mutate(Smoker = factor(if_else(grepl("_S", final_df$group, fixed = TRUE), 'smoker', 'non-smoker'))) %>%
  mutate(Disease = factor(if_else(grepl("HIV", final_df$group, fixed = TRUE), 'HIV', 'SN'))) %>%
  mutate(Sex = if_else(grepl("M", final_df$sex, fixed = TRUE), 1, 0)) %>%
  mutate(Nic_duration_cent = (Nic_duration - mean(Nic_duration, na.rm=TRUE))/sd(Nic_duration, na.rm=TRUE)) %>%
  mutate(Nic_duration_cent = replace(Nic_duration_cent, is.na(Nic_duration_cent) & Smoker == 'non-smoker', 0)) %>%
  mutate(Nic_duration = replace(Nic_duration, is.na(Nic_duration) & Smoker == 'non-smoker', 0)) %>%
  mutate(Nic_lifetime_use_cent = (Nic_lifetime_use - mean(Nic_lifetime_use, na.rm=TRUE))/sd(Nic_lifetime_use, na.rm=TRUE)) %>%
  mutate(Nic_lifetime_use_cent = replace(Nic_lifetime_use_cent, is.na(Nic_lifetime_use_cent) & Smoker == 'non-smoker', 0)) %>%
  mutate(cd8_cent = (cd8 - mean(cd8, na.rm=TRUE))/sd(cd8, na.rm=TRUE)) %>%
  mutate(cd8_cent = replace(cd8_cent, is.na(cd8_cent) & Disease == 'SN', 0)) %>%
  mutate(cd_ratio_cent = (`cd4/cd8` - mean(`cd4/cd8`, na.rm=TRUE))/sd(`cd4/cd8`, na.rm=TRUE)) %>%
  mutate(cd_ratio_cent = replace(cd_ratio_cent, is.na(cd_ratio_cent) & Disease == 'SN', 0)) %>%
  mutate(nadir_cd4_cent = (nadir_cd4 - mean(nadir_cd4, na.rm=TRUE))/sd(nadir_cd4, na.rm=TRUE)) %>%
  mutate(nadir_cd4_cent = replace(nadir_cd4_cent, is.na(nadir_cd4_cent) & Disease == 'SN', 0)) %>%
  mutate(cd4_cent = (cd4 - mean(cd4, na.rm=TRUE))/sd(cd4, na.rm=TRUE)) %>%
  mutate(cd4_cent = replace(cd4_cent, is.na(cd4_cent) & Disease == 'SN', 0)) %>%
  mutate(ViralLoad_cent = (ViralLoad - mean(ViralLoad, na.rm=TRUE))/sd(ViralLoad, na.rm=TRUE))%>%
  mutate(ViralLoad_cent = replace(ViralLoad_cent, is.na(ViralLoad_cent) & Disease == "SN", 0)) %>%
  mutate(Log_VL_cent = (Log_VL - mean(Log_VL, na.rm=TRUE))/sd(Log_VL, na.rm=TRUE)) %>%
  mutate(Log_VL_cent = replace(Log_VL_cent, is.na(Log_VL_cent) & Disease == "SN", 0)) %>%
  mutate(HIVDuration_cent = (`HIVDuration(mons)` - mean(`HIVDuration(mons)`, na.rm=TRUE))/sd(`HIVDuration(mons)`, na.rm=TRUE)) %>%
  mutate(HIVDuration_cent = replace(HIVDuration_cent, is.na(HIVDuration_cent) & Disease == 'SN', 0)) %>%
  mutate(Age_cent = (age - mean(age, na.rm=TRUE))/sd(age, na.rm=TRUE)) %>% 
  mutate(HIV_negative = if_else(grepl("HIV", final_df$group, fixed=TRUE), 0, 1)) %>%
  mutate(Smoker_negative = if_else(grepl("_S", final_df$group, fixed=TRUE), 0, 1))
```
Summary Statistics
```{r}
final_df_new %>%
  group_by(group) %>%
  get_summary_stats(c(age), type="min")

with(final_df_new, table(group, sex))
```
Setting up sub-dataframes
```{r}

thalamus_outliers <- final_df_new %>%
  group_by(Disease, Smoker) %>%
  identify_outliers(trans_Thalamus)
 
final_df_thalamus <- final_df_new[which(!(final_df_new$Row.names%in%thalamus_outliers$Row.names)), ]

final_df_smokers <- final_df_new[final_df_new$Smoker == "smoker",]
final_df_nonsmokers <- final_df_new[final_df_new$Smoker == "non-smoker",]
final_df_HIV <- final_df_new[final_df_new$Disease == "HIV",]
final_df_healthy <- final_df_new[final_df_new$Disease == "SN",]
final_df_HIV_smokers <- final_df_HIV[final_df_HIV$Smoker == "smoker",]
final_df_HIV_nonsmokers <- final_df_HIV[final_df_HIV$Smoker == "non-smoker",]

final_df_smokers_no <- final_df_thalamus[final_df_thalamus$Smoker == "smoker",]
final_df_nonsmokers_no <- final_df_thalamus[final_df_thalamus$Smoker == "non-smoker",]
final_df_HIV_no <- final_df_thalamus[final_df_thalamus$Disease == "HIV",]
final_df_healthy_no <- final_df_thalamus[final_df_thalamus$Disease == "SN",]
```
ANOVA TYPE I
```{r}
anova_results_untransformed_typeI <- purrr::map(final_df_new[,2:12], ~aov(.x ~ Disease * Smoker, data=final_df_new))
lapply(anova_results_untransformed_typeI,function(x)summary(x))
```
ANOVA TYPE II
```{r}
anova_results_typeII <- purrr::map(final_df_new[,2:12], ~Anova(lm(.x ~ Disease * Smoker, data = final_df_new), type="II"))
lapply(anova_results_typeII,function(x)x)
```
TUKEY'S HSD
```{r}
summary(aov(Thalamus ~ group, data=final_df_new))
TukeyHSD(aov(Thalamus ~ group, data=final_df_new))
```
Displaying ANOVA and HSD Results
```{r}
stat.test <- tibble::tribble(
  ~group1, ~group2, ~p.adj,
  "SN_S", "HIV", 0.0206,
  "HIV_S", "SN", 0.0336,
  "SN_S", "HIV_S", 0.00006
)
 
ggboxplot(final_df_new, x = "group", y = "Thalamus", fill="gray", order=c("SN","SN_S","HIV","HIV_S")) + 
  xlab("Group") +
  ylab("rs-CVR in Thalamus ROI") +
  labs(fill = "HIV Status") + 
  scale_x_discrete(labels = c("HIV-negative\nnonsmokers", "HIV-negative\nsmokers"," HIV-positive\nnonsmokers", "HIV-positive\nsmokers")) +
  stat_pvalue_manual(
    stat.test,
    y.position = 1.8,
    step.increase = 0.1,
    label = "p = {p.adj}"
  )
  theme_classic()
```
KRUSKAL + WILCOX (Nonparametric ANOVA and Tukey's HSD)
```{r}
kruskal_results <- purrr::map(final_df_new[,2:12], ~kruskal.test(.x ~ group, data = final_df_new))
lapply(kruskal_results,function(x)x)

art_results <- purrr::map(final_df_new[,2:12], ~art(.x ~ Disease * Smoker, data=final_df_new))
lapply(art_results,function(x)anova(x))

SNnonsmoker_vs_SNsmoker = wilcox.test(final_df_new[final_df_new$Disease == "SN" & final_df_new$Smoker == "non-smoker",]$Thalamus, final_df_new[final_df_new$Disease == "SN" & final_df_new$Smoker == "smoker",]$Thalamus)$p.value
SNnonsmoker_vs_HIVnonsmoker = wilcox.test(final_df_new[final_df_new$Disease == "SN" & final_df_new$Smoker == "non-smoker",]$Thalamus, final_df_new[final_df_new$Disease == "HIV" & final_df_new$Smoker == "non-smoker",]$Thalamus)$p.value
SNnonsmoker_vs_HIVsmoker = wilcox.test(final_df_new[final_df_new$Disease == "SN" & final_df_new$Smoker == "non-smoker",]$Thalamus, final_df_new[final_df_new$Disease == "HIV" & final_df_new$Smoker == "smoker",]$Thalamus)$p.value
SNsmoker_vs_HIVnonsmoker = wilcox.test(final_df_new[final_df_new$Disease == "SN" & final_df_new$Smoker == "smoker",]$Thalamus, final_df_new[final_df_new$Disease == "HIV" & final_df_new$Smoker == "non-smoker",]$Thalamus)$p.value
SNsmoker_vs_HIVsmoker = wilcox.test(final_df_new[final_df_new$Disease == "SN" & final_df_new$Smoker == "smoker",]$Thalamus, final_df_new[final_df_new$Disease == "HIV" & final_df_new$Smoker == "smoker",]$Thalamus)$p.value
HIVnonsmoker_vs_HIVsmoker = wilcox.test(final_df_new[final_df_new$Disease == "HIV" & final_df_new$Smoker == "non-smoker",]$Thalamus, final_df_new[final_df_new$Disease == "HIV" & final_df_new$Smoker == "smoker",]$Thalamus)$p.value
p.adjust(c(SNnonsmoker_vs_HIVnonsmoker, HIVnonsmoker_vs_HIVsmoker, SNsmoker_vs_HIVnonsmoker, SNnonsmoker_vs_HIVsmoker, SNnonsmoker_vs_SNsmoker, SNsmoker_vs_HIVsmoker), method="holm")
```
Regression Analysis
```{r}
# All subjects: final_df_new
# smokers: final_df_smokers
# nonsmokerS: final_df_nonsmokers
# HIV-: final_df_healthy
# HIV+: final_df_HIV
# Untransformed data: [,2:12]
# Transformed data: [,(ncol(final_df_healthy_no)-10):(ncol(final_df_healthy))]

# + Nic_duration_cent:ViralLoad_cent + Smoker_negative:HIV_negative

# + Age_cent:Nic_duration_cent + Age_cent:ViralLoad_cent + Nic_duration_cent:ViralLoad_cent + Smoker_negative:HIV_negative + Age_cent:nadir_cd4_cent

model <- lm(Thalamus ~ Age_cent * nadir_cd4_cent + Age_cent * Nic_duration_cent, data = final_df_new)

summary(model)

tidy(model) %>%
  select(term, estimate, p.value)
```
Plot
```{r}
HIV_neg <- lm(BasalForebrain ~ Age_cent + Nic_duration_cent + Smoker_negative + Age, data = final_df_healthy)

HIV_pos <- lm(Thalamus ~ Age_cent * nadir_cd4_cent, data = final_df_HIV)

neg <- function(x){coef(HIV_neg)[3]*x+coef(HIV_neg)[1]}
pos <- function(x){coef(HIV_pos)[3]*x+coef(HIV_pos)[1]}
coef_neg <- summary(HIV_neg)$coefficients[3,4]
coef_pos <- summary(HIV_pos)$coefficients[3,4]

ggplot(data=final_df_smokers)+
  geom_point(aes(x=Nic_duration_cent, y=BasalForebrain, color=Disease)) +
  stat_function(fun=neg, aes(color = "SN")) + 
  stat_function(fun=pos, aes(color = "HIV")) + 
  xlab("Smoking Duration \n (mean centered and scaled by standard deviation)") +
  ylab("rs-CVR in BasalForebrain ROI") +
  labs(colour = "Disease Status") + 
  annotate("text", x=2.1, y=0.95, label=paste("p =", round(coef_neg,4))) + 
  annotate("text", x=2.1, y=1, label=paste("p =", round(coef_pos,4))) +
  scale_colour_grey(labels = c("HIV Positive", "HIV Negative")) +
  theme_classic()

tidy(HIV_neg) %>%
  select(term, estimate, p.value)

tidy(HIV_pos) %>%
  select(term, estimate, p.value)
```
Plot
```{r}
HIV_pos <- lm(Thalamus ~ Age_cent * nadir_cd4_cent, data = final_df_HIV)
summary(HIV_pos)
pos <- function(x){coef(HIV_pos)[3]*x+coef(HIV_pos)[1]}
coef_pos <- summary(HIV_pos)$coefficients[3,4]

ggplot(data=final_df_HIV)+
  geom_point(aes(x=nadir_cd4_cent, y=Thalamus))+
  stat_function(fun=pos)+
  xlab("nadir CD4 \n (mean centered and scaled by standard deviation)") +
  ylab("rs-CVR in Thalamus ROI") +
  labs(colour = "Disease Status") + 
  annotate("text", x=4, y=0.8, label=paste("p =", round(coef_pos,4))) +
  scale_colour_grey(labels = c("HIV Positive", "HIV Negative")) +
  theme_classic()

tidy(HIV_pos) %>%
  select(term, estimate, p.value)
```
Plot
```{r}
smoke_pos <- lm(BasalForebrain ~ Age_cent * Nic_duration_cent, data = final_df_smokers)
summary(smoke_pos)
pos <- function(x){coef(smoke_pos)[3]*x+coef(smoke_pos)[1]}
coef_pos <- summary(smoke_pos)$coefficients[3,4]

ggplot(data=final_df_smokers)+
  geom_point(aes(x=Nic_duration_cent, y=BasalForebrain))+
  stat_function(fun=pos)+
  xlab("Smoking duration \n (mean centered and scaled by standard deviation)") +
  ylab("rs-CVR in Basal Forebrain ROI") +
  labs(colour = "Disease Status") + 
  annotate("text", x=2, y=0.8, label=paste("p =", round(coef_pos,4))) +
  scale_colour_grey(labels = c("HIV Positive", "HIV Negative")) +
  theme_classic()

# plot_model(smoke_pos, type = "pred", terms = c("Age_cent", "Nic_duration_cent"))

tidy(smoke_pos) %>%
  select(term, estimate, p.value)
```

